Optimal (Multiway) Spatial Joins

### 2024-05-30 msj.tex
yufei

Next, we will prove that a segment $h \in \cross_H(r^*)$ if and only if $h \in \dcross_H(\bm{t})$. Let us start with the ``only-if direction'': assuming $h \in \cross_H(r^*)$, we aim to show $h \in \dcross_H(\bm{t})$. For this purpose, we need to show that $h$ crosses both $\gbot(\bm{t}) = r'$ and $B_\bm{t}$.
\myitems {
    \item First, we explain why $h$ crosses $r'$. Because $r'$ covers $r^*$, by the fact $h$ crossing $r^*$, we know that $h$ must intersect with $r'$. On the other hand, as $h$ crosses $r^*$, it must hold that $\xleft(h) < x_1 < x_2 < \xright(h)$ (recall that $[x_1, x_2]$ is the x-range of $r^*$). As $[x_1, x_2]$ is also the x-range of $r'$, using the fact of $h \cap r' \ne \emptyset$, we can assert that $h$ crosses $r'$.

@@

    Since $\gbot(\bm{t}) = r'$, the bottom edge of $B_{\bm{t}}$ must be contained in $r'$. Thus, $\xleft(B_{\bm{t}})\in [x_1,x_2]$. As proved earlier, $\xleft(h) < x_1 < x_2 < \xright(h)$, which leads to $\xleft(B_{\bm{t}}) \in [\xleft(h), \xright(h)]$, suggesting $p \in h$.

>>>>

Next, we will prove that a segment $h \in \cross_H(r^*)$ if and only if $h \in \dcross_H(\bm{t})$. Let us start with the ``only-if direction'': assuming $h \in \cross_H(r^*)$, we aim to show $h \in \dcross_H(\bm{t})$. For this purpose, we need to show that $h$ crosses both $\gbot(\bm{t}) = r'$ and $B_\bm{t}$.
\myitems {
    \item First, we explain why $h$ crosses $r'$. Because $r'$ covers $r^*$, by the fact $h$ crossing $r^*$, we know that $h$ must intersect with $r'$. On the other hand, as $h$ crosses $r^*$, it must hold that $\xleft(h) < x_1 \le x_2 < \xright(h)$ (recall that $[x_1, x_2]$ is the x-range of $r^*$). As $[x_1, x_2]$ is also the x-range of $r'$, using the fact of $h \cap r' \ne \emptyset$, we can assert that $h$ crosses $r'$.

@@

    Since $\gbot(\bm{t}) = r'$, the bottom edge of $B_{\bm{t}}$ must be contained in $r'$. Thus, $\xleft(B_{\bm{t}})\in [x_1,x_2]$. As proved earlier, $\xleft(h) < x_1 \le x_2 < \xright(h)$, which leads to $\xleft(B_{\bm{t}}) \in [\xleft(h), \xright(h)]$, suggesting $p \in h$.
